\documentclass[11pt, a4paper, twoside]{article}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
%\usepackage{dsfont} %double dashed fonts%
\usepackage[english]{babel}
\usepackage[pdftex]{graphicx}
\usepackage{color}
\usepackage{subfigure}
\usepackage{listings}
\usepackage[colorlinks]{hyperref}
\usepackage[small]{caption}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amstext}
\usepackage{tikz}
\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds}
\usepackage[hmarginratio=1:2,vmargin=1in]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancy}

\newcommand{\e}{\mathrm{e}} % exponential e
\renewcommand{\d}{\mathrm{d}} % for derivatives
\renewcommand{\vec}[1]{{\boldsymbol #1}}
\newcommand{\dd}[2]{\frac{\d #1}{\d #2}}
\newcommand{\pd}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\degr}[1]{$#1\,^\circ\mathrm{C}$}

\newcommand{\Rth}{R_\mathrm{th}} % to be used within $$!
\newcommand{\Ths}{T_\mathrm{hs}} % to be used within $$!

\numberwithin{equation}{section} %https://www.physicsforums.com/threads/numbering-the-equations-in-latex.324808/
%\numberwithin{equation}{subsection}
\numberwithin{table}{section}
\numberwithin{figure}{section}

\title{Performance of wafer-fused VECSEL under high power operation}
\author{Stefan Keller\\
{\it Master project, Departement Physik, ETH Z\"urich}\\
{\it Dr. Vladimir Iakovlev*,}\\
{\it Dr. Alexei Sirbu*,}\\
{\it Prof. Dr. Eli Kapon*,}\\
{\it Prof. Dr. J\'er\^ome Faist$^+$}\\
\\
*EPF Lausanne, $^+$ETH Z\"urich}
\date{\today}

\begin{document}
\maketitle
\fancyhead[LE]{VECSEL high power performance}
\fancyhead[LO]{\leftmark}
\fancyhead[R]{Stefan Keller}

\begin{abstract}
I report on the performance
of $1300\,\mathrm{nm}$ waveband
wafer-fused vertical-external-cavity
surface-emitting laser (VECSEL)
in a thin disk (flip-chip) heat dissipation scheme.
I investigate on its scaling behavior
concerning output power
and thermal resistance.
The latter is assessed
on whether it provides
a useful tool
for device metrology.
An optimization strategy
concerning one of the manufacturing steps
is evaluated,
and resulted
in the record performance
of $8.5\,\mathrm{W}$
output power
with a conversion efficiency
of $60\,\%$ at \degr{5}
heat sink temperature.
The reflectivity
off our device
is found to change
with heat sink temperature
and pump power.
Last but not least,
the investigated wafer-fused samples
did not show signs of degradation
despite exposure of
inhospitable measurement conditions.
\end{abstract}

%\newpage
\tableofcontents\newpage

\input{src/intro}
\input{src/basics}
\input{src/thermalres}
\input{src/comsol}
\input{src/exp_setup}
\input{src/evaluation}
\input{src/conclusion}

\newpage
\appendix
\input{src/appendix/alignment}
\input{src/appendix/spatial}
\input{src/appendix/comsol_deriv}

\newpage
\input{src/bib}

\end{document}
