\subsection{By roll over}
\label{sec:rth:trollover}

A second method,
relies on an intrinsic roll over temperature.
Roll over is an effect due to the optical pumping:
While increasing the pump power
in order to obtain higher emitted output,
we heat the gain structure.
This increase in temperature
introduces an additional loss
which the gain
has to compensate.
Otherwise,
our device stops lasing.
After a certain point
the gain cannot compensate for the losses anymore,
and this region stops contributing
to the output.
We see
a decline
in output power
despite the higher pump --
a roll-over.

Heinen et al. \cite{Heinen2012}
have found empirically --
using the method described in \ref{sec:rth:lambda} --
the longest wavelength
at this roll over point
is the same wavelength,
regardless of the heat sink temperature.
They conclude,
this wavelength to correspond
to an of the structure intrinsic
critical temperature --
the roll over temperature.
Given definition (\ref{eq:rth})
we find
the difference in temperature
between (unknown) roll over and heat sink.
It is
the thermal resistance
times the dissipated power,
\begin{equation}
T_\mathrm{ro} - \Ths = \Rth D_\mathrm{ro}.
\end{equation}
In other words,
when we plot
dissipated power at roll over ($D_\mathrm{ro}$)
versus the heat sink temperature
for this measurement $\Ths$,
we find a linear relation.
Its slope corresponds
to the thermal resistance,
and the $y$-intersection
to the roll over temperature \cite{Heinen2012}:
\begin{equation}
\Ths = -\Rth D_\mathrm{ro} + T_\mathrm{ro}.
\end{equation}

This relation is wavelength independent.
Mode instabilities in pump and emission
are expected to result in fluctuations
in the emitted spectra.
A spectrum independent method
to determine $\Rth$ is thus supposed to
yield a result with smaller uncertainty.
The difficulties in this second method
arise from identifying
the exact point of roll over.
Whether this identification
is more or less error-prone
is open for discussion.
Furthermore,
it is not yet clear
whether all VECSEL designs
show this intrinsic roll over behavior.