\section{Surface temperature raise, numerically}
\label{sec:comsol}

The commercial software COMSOL
allows us to perform thermal simulations
with a finite-element approach.
The heat equation
to be solved
reads as
\begin{equation}
0 = \nabla(k\nabla T) + Q.
\label{eq:heateq}
\end{equation}
It is $k$ the thermal conductivity of the material
($[k]=\mathrm{m}^{-1}$),
and $Q$ the heat source
($[Q]=\mathrm{W}/\mathrm{m}^3$);
originating from the pump beam.
With this equation we take into account
only conduction
and ignore convection.
In anisotropic materials
the thermal conductivity differs
depending on the direction of conduction.
For the simulation we assume radial symmetry,
in order to bring the 3D problem down to 2D.
This saves computation time.

In this section,
I cover some numerical considerations
regarding the pump induced
temperature increase
within the different layers
of a VECSEL structure.
The presented plots
show the expected temperature profile
along the most important interface:
the top of the gain section \cite{Ranta2014OptLett}.

I only describe
the new considerations
made in the course
of this project.
While in appendix~\ref{app:comsol_deriv},
I explain
where the formulae come from
that are widely used in literature
\cite{Ranta2014OptLett,Kemp2008,Kemp2005,Vetter2012,Lindberg2005}.
This appendix also provides
additional insights,
necessary to properly implement
our structure in COMSOL.
I start by introducing
a beam profile
that was so far not considered
in these investigations.
Eventually,
I present
the calculated
pump induced temperature increase
along the surface of the gain layer
of our VECSEL structure,
considering different pump powers
and pump beam profiles.



\input{src/comsol/beamprofile}
\input{src/comsol/tempincrease}



